Seasonality in governing dynamics at submesoscales in the Kuroshio Extension

### 2016-06-28 writeup/rocha_etal.tex
Small edit and change fig size

\begin{figure*}[ht]
\begin{center}
\hspace{-1.25cm}\includegraphics[width=.6\textwidth]{figs/fig1_1.pdf}\\
\vspace{-.125cm}
\includegraphics[width=.65\textwidth]{figs/fig1_2.pdf}
 \caption{(a) The study region with the subregion where the LLC outputs are
          analyzed. Colors represent the topography and white lines are contours of absolute
          dynamic topography every 0.1 m. LLC 4320 (1/48$^\circ$) snapshots of surface vorticity (b and c) and a transect
          of potential density at 165$^\circ$E (d and e). The snapshots were
          taken at 00:00 UTC.}
\vspace{-1.5cm}
 \label{fig1}
 \end{center}
 \end{figure*}

@@

 \begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.65\textwidth]{figs/fig2.pdf}
  \caption{Time series of the root-mean-square (RMS) of vorticity (a) and
  rate of strain (b), and horizontal divergence (c) in the LLC outputs and gridded AVISO data.}
  \label{fig2}
  \end{center}
\end{figure*}

The bulk of vertical vorticity and lateral strain rate are associated with subinertial flows
($T_f = 2\pi/f_0\approx 23.5$h, where $f_0$ is the inertial frequency at
the mean latitude): daily-averaging the velocity fields suppresses superinertial
motions and reduces the RMS
vorticity by less than 40$\%$ and the RMS strain by less than 10$\%$; the seasonal
cycle remains strong (see
dashed lines in figures \ref{fig2}a-b). Most of this seasonal cycle is associated
with submesoscale flows: smoothing the velocity fields
with a Hanning filter with cut-off scale of 100 km dramatically reduces the RMS
vorticity and strain. The reduction in variance is about 80$\%$ in winter,
yielding RMS vorticity and strain roughly consistent with the diagnostics from
AVISO gridded geostrophic velocities (compare red lines to black lines in figures \ref{fig2}a-b).
The picture that emerges is consistent with recent studies: shallow baroclinic
instabilities energize the submesoscales in late Winter, drawing from the available
potential energy stored in deep mixed layers \citep{sasaki_etal2014,callies_etal2015,callies_etal2016}.

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.75\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}

@@

These high-frequency submesoscale flows significantly project on the sea-surface.
In October, when the inertia-gravity waves are strongest the surface and submesoscale
turbulence is weakest. There is a dramatic difference between the spectra
based on hourly and daily-averaged SSH: at scales smaller than 100 km, the spectra
of hourly SSH roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
SSH roughly follows a $-5$ power-law. At these scales, 33$\%$ of the SSH variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October! Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface inertia-gravity waves conspire to yield very weak seasonality
in the spectra of KE and SSH variance based on hourly fields.

>>>>

\begin{figure*}[ht]
\begin{center}
\hspace{-1.25cm}\includegraphics[width=.75\textwidth]{figs/fig1_1.pdf}\\
\vspace{-.125cm}
\includegraphics[width=.75\textwidth]{figs/fig1_2.pdf}
 \caption{(a) The study region with the subregion where the LLC outputs are
          analyzed. Colors represent the topography and white lines are contours of absolute
          dynamic topography every 0.1 m. LLC 4320 (1/48$^\circ$) snapshots of surface vorticity (b and c) and a transect
          of potential density at 165$^\circ$E (d and e). The snapshots were
          taken at 00:00 UTC.}
\vspace{-1.5cm}
 \label{fig1}
 \end{center}
 \end{figure*}

@@

 \begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.75\textwidth]{figs/fig2.pdf}
  \caption{Time series of the root-mean-square (RMS) of vorticity (a) and
  rate of strain (b), and horizontal divergence (c) in the LLC outputs and gridded AVISO data.}
  \label{fig2}
  \end{center}
\end{figure*}

The bulk of vertical vorticity and strain rate are associated with subinertial flows
($T_f = 2\pi/f_0\approx 23.5$h, where $f_0$ is the inertial frequency at
the mean latitude): daily-averaging the velocity fields suppresses superinertial
motions and reduces the RMS
vorticity by less than 40$\%$ and the RMS strain by less than 10$\%$; the seasonal
cycle remains strong (see
dashed lines in figures \ref{fig2}a-b). Most of this seasonal cycle is associated
with submesoscale flows: smoothing the velocity fields
with a Hanning filter with cut-off scale of 100 km dramatically reduces the RMS
vorticity and strain. The reduction in variance is about 80$\%$ in winter,
yielding RMS vorticity and strain roughly consistent with the diagnostics from
AVISO gridded geostrophic velocities (compare red lines to black lines in figures \ref{fig2}a-b).
The picture that emerges is consistent with recent studies: shallow baroclinic
instabilities energize the submesoscales in late Winter, drawing from the available
potential energy stored in deep mixed layers \citep{sasaki_etal2014,callies_etal2015,callies_etal2016}.

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}

@@

The inertia-gravity waves significantly project on the sea-surface.
In October, when the inertia-gravity waves are strongest the surface and submesoscale
turbulence is weakest. There is a dramatic difference between the spectra
based on hourly and daily-averaged SSH: at scales smaller than 100 km, the spectra
of hourly SSH roughly follows a $-2$ power-law, whereas the spectra of daily-averaged
SSH roughly follows a $-5$ power-law. At these scales, 33$\%$ of the SSH variance in April is accounted for by super-inertial
flows as opposed to 83$\%$ in October! Curiously, the out-of-phase seasonal cycle of submesoscale
turbulence and near-surface inertia-gravity waves conspire to yield very weak seasonality
in the spectra of KE and SSH variance based on hourly fields.
